---
title: "Telco Customer Churn Prediction - Logistic Regression"
output: html_notebook
---
Loading required packages
```{r}
#install.packages("ROCR")
library(ggplot2)
library(corrplot)
library(ROCR)
```


```{r}
getwd()
```

Reading input file
```{r}
data.set.orig = read.csv(file = "Datasets/Teleco_Cust_Attr.csv", header = T)
```
```{r}
head(data.set.orig)
```


```{r}
summary(data.set.orig)
```
Data Preprocessing

Dropping customerID variable

```{r}
data.set.orig$customerID = NULL
```

Checking for Missing Values and imputing
```{r}
sapply(data.set.orig, function(x) sum(is.na(x)))
```

Handling NAs in TotalCharges
```{r}
data.set.orig$TotalCharges = ifelse(is.na(data.set.orig$TotalCharges),
                                    data.set.orig$tenure*data.set.orig$MonthlyCharges,
                                    data.set.orig$TotalCharges)
sapply(data.set.orig, function(x) sum(is.na(x)))
```

Converting SeniorCitizen to factor
```{r}
data.set.orig$SeniorCitizen = as.factor(data.set.orig$SeniorCitizen)
```

EDA

```{r}
i=1
for(i in 1:ncol(data.set.orig)){
  #print(colnames(data.set.orig)[i])
  if(is.factor(data.set.orig[,i])){
    print(ggplot(data.set.orig,aes_string("Churn",colnames(data.set.orig)[i]))
          +geom_jitter(aes(col=Churn)))
  }
}
```

```{r}
i=1
for(i in 1:ncol(data.set.orig)){
  #print(colnames(data.set.orig)[i])
  if(is.numeric(data.set.orig[,i])){
    print(ggplot(data.set.orig,aes_string(colnames(data.set.orig)[i]))
          +geom_density())
  }
}
```

```{r}
nums = unlist(lapply(data.set.orig, is.numeric))  
temp = data.set.orig[,nums]
price.corplot = cor(temp)
corrplot(price.corplot, method="number")  
```
```{r}
print(ggplot(data.set.orig,aes(Churn,tenure))+geom_boxplot())
```


Dropping variables tenure and MonthlyCharges
```{r}
#data.set.orig$tenure = NULL
#data.set.orig$MonthlyCharges = NULL
```

```{r}
head(data.set.orig)
```

Transforming TotalCharges to Normal Distribution
```{r}
print(ggplot(data.set.orig,aes(TotalCharges))+geom_density())
print(ggplot(data.set.orig,aes(sqrt(TotalCharges)))+geom_density())
print(ggplot(data.set.orig,aes(Churn,TotalCharges))+geom_boxplot())
```

```{r}
print(ggplot(data.set.orig,aes(tenure))+geom_density())
print(ggplot(data.set.orig,aes(sin(tenure)))+geom_density())
print(ggplot(data.set.orig,aes(Churn,tenure))+geom_boxplot())
print(ggplot(data.set.orig[data.set.orig$tenure<30,],aes((tenure)))+geom_density())
print(ggplot(data.set.orig[data.set.orig$tenure<30,],aes(sqrt(tenure)))+geom_density())
```
```{r}
print(ggplot(data.set.orig,aes(MonthlyCharges))+geom_density())
print(ggplot(data.set.orig,aes(sqrt(MonthlyCharges)))+geom_density())
print(ggplot(data.set.orig,aes(Churn,MonthlyCharges))+geom_boxplot())
```
Subsetting Required Variables
```{r}
colnames(data.set.orig)
data.set = data.set.orig[,c("SeniorCitizen","Dependents","PhoneService","MultipleLines","InternetService" , "OnlineSecurity"  , "OnlineBackup","DeviceProtection" ,"TechSupport"   ,   "StreamingTV" ,     "StreamingMovies" , "Contract","PaperlessBilling", "PaymentMethod"  , "tenure","Churn")]
```


Test Train Split
```{r}
sample = sample(1:nrow(data.set),0.7*nrow(data.set))
train.data.set = data.set[sample,]
test.data.set = data.set[-sample,]
rbind(nrow(data.set),nrow(train.data.set),nrow(test.data.set))

```

Applying Logistic Regression
```{r}
m1 <- glm (Churn ~ ., data = train.data.set, family = binomial)
summary(m1)
```
```{r}
p1 = predict(m1, train.data.set, type = 'response')
pred2 = prediction(p1,train.data.set$Churn)
perf = performance(pred2,"tpr","fpr")
plot(perf,colorize = T)
t1 = table(train.data.set$Churn, p1 > 0.45)
t1
TN1 = t1[1]
FN1 = t1[2]
FP1 = t1[3]
TP1 = t1[4]

TN1
FN1
FP1
TP1

Accuary1 = (TP1+TN1)/(TP1+TN1+FP1+FN1)
Precision1 = (TP1)/(TP1+FP1)
Recall1 = (TP1)/(TP1+FN1)
F11 = 2*Precision1*Recall1/(Precision1+Recall1)

Accuary1
Precision1
Recall1
F11
```

```{r}
p1 = predict(m1, test.data.set, type = 'response')
pred2 = prediction(p1,test.data.set$Churn)
perf = performance(pred2,"tpr","fpr")
plot(perf,colorize = T)


t1 = table(test.data.set$Churn, p1 > 0.45)
t1
TN1 = t1[1]
FN1 = t1[2]
FP1 = t1[3]
TP1 = t1[4]

TN1
FN1
FP1
TP1

Accuary1 = (TP1+TN1)/(TP1+TN1+FP1+FN1)
Precision1 = (TP1)/(TP1+FP1)
Recall1 = (TP1)/(TP1+FN1)
F11 = 2*Precision1*Recall1/(Precision1+Recall1)

Accuary1
Precision1
Recall1
F11
```

Model 2
Subsetting Required Variables
```{r}
colnames(data.set.orig)
data.set = data.set.orig[,c("SeniorCitizen","Dependents","Partner","PhoneService","MultipleLines","InternetService" , "OnlineSecurity"  , "OnlineBackup","DeviceProtection"  ,   "StreamingTV" , "Contract", "PaymentMethod"  , "tenure","Churn")]
```


Test Train Split
```{r}
sample = sample(1:nrow(data.set),0.7*nrow(data.set))
train.data.set = data.set[sample,]
test.data.set = data.set[-sample,]
rbind(nrow(data.set),nrow(train.data.set),nrow(test.data.set))

```

Applying Logistic Regression
```{r}
m1 <- glm (Churn ~ ., data = train.data.set, family = binomial)
summary(m1)
```


```{r}
p1 = predict(m1, train.data.set, type = 'response')
pred2 = prediction(p1,train.data.set$Churn)
perf = performance(pred2,"tpr","fpr")
plot(perf,colorize = T)
t1 = table(train.data.set$Churn, p1 > 0.45)
t1
TN1 = t1[1]
FN1 = t1[2]
FP1 = t1[3]
TP1 = t1[4]

TN1
FN1
FP1
TP1

Accuary1 = (TP1+TN1)/(TP1+TN1+FP1+FN1)
Precision1 = (TP1)/(TP1+FP1)
Recall1 = (TP1)/(TP1+FN1)
F11 = 2*Precision1*Recall1/(Precision1+Recall1)

Accuary1
Precision1
Recall1
F11
```

```{r}
p1 = predict(m1, test.data.set, type = 'response')
pred2 = prediction(p1,test.data.set$Churn)
perf = performance(pred2,"tpr","fpr")
plot(perf,colorize = T)


t1 = table(test.data.set$Churn, p1 > 0.45)
t1
TN1 = t1[1]
FN1 = t1[2]
FP1 = t1[3]
TP1 = t1[4]

TN1
FN1
FP1
TP1

Accuary1 = (TP1+TN1)/(TP1+TN1+FP1+FN1)
Precision1 = (TP1)/(TP1+FP1)
Recall1 = (TP1)/(TP1+FN1)
F11 = 2*Precision1*Recall1/(Precision1+Recall1)

Accuary1
Precision1
Recall1
F11
```



